### 2018-09-02 sections/objects.tex
toronto textual comments part 1
more textual comments and bib formatting

Electron candidates~\cite{ATLAS-CONF-2016-024,ATL-PHYS-PUB-2016-015} are reconstructed from energy 
clusters in the EM calorimeter that are matched to reconstructed tracks in the inner detector;
electron candidates in the transition region between the EM barrel and endcap calorimeters 
($1.37 < |\eta_{\textrm{cluster}}| < 1.52$) are excluded.
In the $\Hbb$ ($\Htautau$) search, electron candidates are required to have $\pt>30~(15)~\gev$ and 
$|\eta_{\textrm{cluster}}| < 2.47$, and to satisfy tight (medium) likelihood-based identification 
criteria~\cite{ATLAS-CONF-2016-024} based on calorimeter, tracking and combined variables that provide 
separation between electrons and jets. 
Muon candidates~\cite{Aad:2016jkr} are reconstructed by matching track segments in %the various
different layers of the muon spectrometer to tracks found in the inner detector;
the resulting muon candidates are refitted using the complete track information from both detector systems.
In the $\Hbb$ ($\Htautau$) search, muon candidates are required to have $\pt>30~(10)~\gev$ and $|\eta|<2.5$ 
and to satisfy medium identification criteria~\cite{Aad:2016jkr}.

@@

%a Gradient isolation working points are used for both electrons and muons. The working points are based on cut maps derived from the $Z\to l^+l^-$ Monte Carlo samples. The efficiency maps are simply derived from the sum of transverse energy of the clusters deposited in the calorimeter in the given cone. The efficiency for the leptons with a certain $\pt$ is $(0.1143*\pt[\GeV]+92.14)\%*(0.1143*\pt[\GeV]+92.14)\%$.

Candidate jets are reconstructed with the anti-$k_t$ algorithm~\cite{Cacciari:2008gp,Cacciari:2005hq,Cacciari:2011ma} with a
radius parameter $R=0.4$, using topological clusters~\cite{Aad:2016upy} 
built from energy deposits in the calorimeters calibrated to the electromagnetic scale. 
The reconstructed jets are then calibrated to the particle level by the application of a jet energy scale 
derived from simulation and {\textit{in situ}} corrections based on $\sqrt{s}=13~\tev$ data~\cite{Aaboud:2017jcu}.
The calibrated jets used by the $\Hbb$ search are required to have $\pt > 25~\gev$ and $|\eta| < 2.5$,
while the $\Htautau$ search uses jets with $\pt > 30~\gev$ and $|\eta| < 4.5$.
Quality criteria are imposed to reject events that contain any jets arising from non-collision sources
or detector noise~\cite{ATLAS-CONF-2015-029}.  To reduce the contamination due to jets originating from pile-up interactions,
additional requirements are made on the Jet Vertex Tagger (JVT)~\cite{Aad:2015ina} output for jets with $\pt<60~\gev$ and $|\eta| < 2.4$,
or on the forward JVT~\cite{Aaboud:2017pou} output for jets with $\pt<50~\gev$ and $|\eta| > 2.5$.

>>>>

Electron candidates~\cite{ATLAS-CONF-2016-024,ATL-PHYS-PUB-2016-015} are reconstructed from energy 
clusters in the EM calorimeter that are matched to reconstructed tracks in the inner detector;
electron candidates in the transition region between the EM barrel and endcap calorimeters 
($1.37 < |\eta_{\textrm{cluster}}| < 1.52$) are excluded.
In the $\Hbb$ ($\Htautau$) search, electron candidates are required to have $\pt>30~(15)~\gev$ and 
$|\eta_{\textrm{cluster}}| < 2.47$, and to satisfy tight (medium) likelihood-based identification 
criteria~\cite{ATLAS-CONF-2016-024} based on calorimeter, tracking and combined variables that provide 
separation between electrons and jets.

Muon candidates~\cite{Aad:2016jkr} are reconstructed by matching track segments in %the various
different layers of the muon spectrometer to tracks found in the inner detector;
the resulting muon candidates are refitted using the complete track information from both detector systems.
In the $\Hbb$ ($\Htautau$) search, muon candidates are required to have $\pt>30~(10)~\gev$ and $|\eta|<2.5$ 
and to satisfy medium identification criteria~\cite{Aad:2016jkr}.

@@

%a Gradient isolation working points are used for both electrons and muons. The working points are based on cut maps derived from the $Z\to l^+l^-$ Monte Carlo samples. The efficiency maps are simply derived from the sum of transverse energy of the clusters deposited in the calorimeter in the given cone. The efficiency for the leptons with a certain $\pt$ is $(0.1143*\pt[\GeV]+92.14)\%*(0.1143*\pt[\GeV]+92.14)\%$.
%draft 1 version
%Candidate jets are reconstructed with the anti-$k_t$ algorithm~\cite{Cacciari:2008gp,Cacciari:2005hq,Cacciari:2011ma} with a
%radius parameter $R=0.4$, using topological clusters~\cite{Aad:2016upy} 
%built from energy deposits in the calorimeters calibrated to the electromagnetic scale. 
Candidate jets are reconstructed with the anti-$k_t$ algorithm~\cite{Cacciari:2008gp,Cacciari:2005hq} with a
radius parameter $R=0.4$, as implemented in the \fastjet\ package~\cite{Cacciari:2011ma}.  
Jet reconstruction in the calorimeter starts from topological clustering~\cite{Aad:2016upy} of individual calorimeter cells calibrated to the electromagnetic scale. 
The reconstructed jets are then calibrated to the particle level by the application of a jet energy scale 
derived from simulation and {\textit{in situ}} corrections based on $\sqrt{s}=13~\tev$ data~\cite{Aaboud:2017jcu}.
The calibrated jets used by the $\Hbb$ search are required to have $\pt > 25~\gev$ and $|\eta| < 2.5$,
while the $\Htautau$ search uses jets with $\pt > 30~\gev$ and $|\eta| < 4.5$.
Quality criteria are imposed to reject events that contain any jets arising from non-collision sources
or detector noise~\cite{ATLAS-CONF-2015-029}.  To reduce the contamination due to jets originating from pile-up interactions,
additional requirements are made on the Jet Vertex Tagger (JVT)~\cite{Aad:2015ina} output for jets with $\pt<60~\gev$ and $|\eta| < 2.4$,
or on the forward JVT~\cite{Aaboud:2017pou} output for jets with $\pt<50~\gev$ and $|\eta| > 2.5$.
